How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-17 tse-paper/content.tex
Add Litsurvey protocol

\textbf{Motivation.}
Continuous Integration (CI) has become a common practice in software
engineering~\cite{hilton2016usage}.  Many software projects use
CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
developer productivity~\cite{miller2008hundred,hilton2016usage} and
communication~\cite{downs2012ambient}.  CI builds produce logs which
report results of various sub-steps within the build.  These build logs
contain a lot of valuable information for developers and researchers---for
example, descriptions of compile errors, linter warnings or failed
tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

@@

>>>>

Continuous Integration (CI) has become a common practice in software
engineering~\cite{hilton2016usage}.  Many software projects use
CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
developer productivity~\cite{miller2008hundred,hilton2016usage} and
communication~\cite{downs2012ambient}.  CI builds produce logs which
report results of various sub-steps within the build.  These build logs
contain a lot of valuable information for developers and researchers---for
example, descriptions of compile errors, linter warnings or failed
tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

@@

\section{Systematic Literature Survey}
\label{sec:survey}
From our own experience, we know that the field of analyzing build
logs is relatively young, with perhaps the work on TravisTorrent the
most cited and central one. We also know there have been scattered
research efforts on build log analysis prior to it, mostly where the
log analysis was a side-part of the article. To the best of our
knowledge, there has not been an attempt to systematically overview
and survey them, despite their forseeable future and current practical
importance.

\subsection{Methodology}
In this first overview, we therefore want to survey as broad a
population of papers, books, and other scientific publications as
possible. One challenge is that no common nomenclature has been
established yet (in fact, this is one of the goals of this
article).

Since we cannot take for granted that ``analyzing build logs'' is the
cannonical term that other, isolated works have used, we instead
decdided to leave out the potentially variable ``analysis'' part and
instead focus on variations of the term ``build log''. This has the
advantage of being biunique: We explicitly decided to include systems
or event logs (see \Cref{sec:rw}). On the other hand, a Google Scholar
search for ``build log'' returns more than 2.2 million results
(2020-03-15). We therefore refined our search criterions for the four
different spelling possibilities of ``build log'' to exclude obvious
non-related works. This left us with 1,552 combined search results
(2020-03-15).

To make handling so many search results feasible, the authors of the
paper employed a two-pass filtering strategy:

First, we filtered out articles based on 1) their title and 2) the
contextual information Google Scholar displayed. Our strategy was to
err on the side of caution, that is rather including a paper than
not. We then unified the search results, removing duplicates. After
this process, we were left with 271 (17\%) of the original search
results.

We did a second filter phase by downloading the remaining papers,
reading their abstracts, and searching the full text for the
occurrence of ``log''. If these papers contained traces of working
with build logs, we included them in our survey.

%todo: fill-in number
Wtih these X remaining articles, we followed a limited backward
snowball sampling for articles referenced in the paragraphs that
mention the technique. Having added these papers to our literature
set, we performed a full forward-snowball sampling for all papers in
the set.
